GVN-Hoist: Hoisting Computations from Branches

### 2016-08-08 hoist.tex
overview of the algorithm

\subsection{Overview}

@@

For legality we have to check that the side-effects of call does not intersect
any side-effect between the instruciton to be hoisted and its hoisting point.

>>>>

@@

\subsection{Overview}
Similar to most compiler optimization passes the code-hoisting can also be
divided into following five steps:

\begin{enumerate}
\item Checking for candidacy. Finding if a set of instructions perform identical
  computation.
\item Checking for legality. Finding a hoisting point i.e. a common dominator of
  the set of instructions. If such a dominator is found then checking if all the
  use-operands of the set of instructions are available or not.  Checking that
  the side-effects of the computations does not intersect any side-effect
  between the instructions to be hoisted and their hoisting point. In some cases
  if the operands are not available, it is possible to reinstantiate
  (remateralize) the use-operands, thus making the passing the legality check.
\item Checking for profitability. Establishing a set of cost models tune for
  performance. Like decreasing code size, minimizing spills etc.
\item Making the transformation. Putting a copy of the computation at the
  hoisting point and removing all the computations made redundant by the new
  copy.
\item Verification. Performing a set of checks (e.g., consistency of use-defs
  and SSA semantics) to establish that program invariants are maintained.
\end{enumerate}
